Influence of Connectivity on Dung Beetle Communities

### 2025-03-03 corridor_docs/eric_ms_thesis/thesis_planning.Rmd
pushibg

```{r Table3, echo=FALSE,message = FALSE,warning=FALSE}
library(iNEXT)

@@

>>>>

```{r Figure 1, echo=FALSE,message = FALSE,warning=FALSE}
library(iNEXT)

@@

```{r Table 3, echo=FALSE,message = FALSE,warning=FALSE}
btl_spec_patch<- btl_data |>
  pivot_longer(pvin:osyl, names_to = "species", values_to = "n") |>
  group_by(species,patch) |>
  summarise(n=sum(n, na.rm=TRUE)) |>
  arrange(patch,desc(n)) |>
  pivot_wider(values_from=n,names_from=species) |>
  mutate(patch=case_when(
    patch == "c" ~ "Corridor",
    patch == "m" ~ "Matrix",
    patch == "w" ~ "Winged",
    patch == "r" ~ "Rectangle",
    .default = as.character(patch))) |>
  column_to_rownames("patch")

taxa_bray <- vegan::vegdist(btl_spec_patch, method = "bray", binary = FALSE)
taxa_bray
